---
title: "interview review for pacific"
author: "JIASHU MIAO"
date: "2/14/2019"
output: html_document
---
```{r}

pkg <- c("readr","readxl","dplyr","stringr","ggplot2","tidyr","stats")
pkgload <- lapply(pkg, require, character.only = TRUE)
```
```{r}
# load the data

load("LAB4PM.RData")
# readxl::read_excel()
# save()
data1 <- LAB4PM

class(data1)
names(data1)
str(data1)
data2 <- select(data1, AnionGap, Age, Year, SODIUM)

colSums(data2, na.rm = T)
dataex1 <- read_excel("/Users/MichaelMiao/Documents/GitHub/R-scripts-/interview/Acumen_Data_Analysis_Exercise.xlsx", sheet = "Data")
str(dataex1)
which(is.na(dataex1$Race))
colSums(is.na(dataex1))
MEANSEX <- mean(dataex1$`Sex (Male=1)`,na.rm = T)
replace(dataex1$`Sex (Male=1)`,is.na(dataex1$`Sex (Male=1)`) , MEANSEX)
is.na(dataex1$`Sex (Male=1)`)

any(is.na(dataex1$`Sex (Male=1)`))
colSums(is.na(dataex1))

?if_else()
?ifelse


```
```{r}
# 8 Write a function in R language to replace the missing value in a vector with the mean of that vector.
x= c(1:20)
x <- replace(x,x>10,NA) #  #!!!!一定要保存
```

```{r}
# 7 How do you split a continuous variable into different groups/ranks in R?
   
as.factor(x)
df <- data.frame(x, y=sample(1:100, 20, replace = F)) 

df
df %>% group_by(x) %>%  summarise_all(.,funs(mean)) 
```
```{r}
# https://blog.revolutionanalytics.com/2012/03/r-and-hadoop-step-by-step-tutorials.html
```

```{r}
# file.show("LAB4PM.RData")
save(data2, file="accumendata.RData")
load("accumendata.RData")

# floating-point numbers (type num); their precision is 0.1 cmol+ (kg soil)-1 .

```

```{r}
dataex2 <- rename(dataex1, Sex = `Sex (Male=1)` )
names(dataex2)
stem(dataex2$Sex)
stem(dataex2$Race)
```

```{r}

  # > hist(Clay1, breaks=seq(0, 96, by=8), col="darkgray", border="black",
  # +     main="Clay proportion in surface soil, weight %")
  # > rug(Clay1)
# 
```

```{r}

?rug
# rug(x, ticksize = 0.03, side = 1, lwd = 0.5, col = par("fg"),
    # quiet = getOption("warn") < 0, ...)
```
```{r}
require(stats)  # both 'density' and its default method
with(faithful, {
    plot(density(eruptions, bw = 0.15))
    # rug(eruptions)
    rug(jitter(eruptions, amount = 0.01), side = 3, col = "light blue")
})

```

```{r}
# two ways to subset
# mtcars
attach(mtcars)
mtcars[disp > 65, ]
(ix <- which(disp > 65))
mtcars[ix, ]
par(mfrow=c(2,2))
```
```{r}
?t.test()
```


```{r}
# sdata2$Age[order(data2$Age)]
# data2$Age
```
```{r}
by(data = data2$Age, data1$Year, range)
#!!! by function 太好用了吧

```
```{r}
# pairwise.t.test(Clay5, zone, p.adj="none",pool.sd=F)
```

```{r}
?par()
par(mfrow=c(2,2))
# par(mfcol=c(1,2))
pairs(data = data2, data2$Year ~data2$Age+data2$AnionGap)
pairs(data = data2, ~data2$Age+data2$AnionGap)

```
```{r}
# > cov(obs[c(10,7,13)])
#                         CEC1   Clay1     OC1
#                CEC1  25.9479  39.609  5.6793
#                Clay1 39.6092 194.213 12.5021
#                OC1    5.6793  12.502  2.2520
#                > cor(obs[c(10,7,13)])
#                         CEC1   Clay1     OC1
#                CEC1  1.00000 0.55796 0.74294
#                Clay1 0.55796 1.00000 0.59780
#                OC1   0.74294 0.59780 1.00000
```
```{r}
# summary(lmcec.null)$adj.r.squared !!这种表达101a

```

```{r}
 # vif(lm(Clay5 ~ Clay1 + CEC1 + OC1 + CEC2 + OC2, data=obs))
# > AIC(lm(Clay5 ~ Clay2 + CEC1 + OC1 + CEC2 + OC2, data=obs)) with higher aic好 reduced odel

```
Q87 : What proportion of the total variance is explained by the first component alone? By the first and second? Jump to A87 •
The numbers here are misleading, because the variables are on different scales. In these cases it is better to compute the standardised components, using the correlation instead of covariance matrix; this standardises all the variables to zero mean and unit standard deviation before computing the components.
Task 59 : Compute the standardized principal components of three variables: topsoil clay, CEC, and organic carbon. •
This option is specified by setting the scale optional argument to TRUE. > pc.s <- prcomp(obs[c(10,7,13)], scale=T)
  > summary(pc.s)
  Importance of components:
                           PC1   PC2    PC3
  Standard deviation     1.506 0.690 0.5044



```{r}

```

















